\section{Requirements}
This chapter identifies global requirements that the system should satisfy. These requirements mostly concern safety of the system but also how the system should function when more boats are demanding to use it. The following requirements will be verified later on the design:

\subsubsection*{Safety}
\begin{enumerate}
	\item Only one gate can be open at a time.
	\item Only one valve can be open at a time.
	\item A valve and a gate at different levels can never be open at the same time.
	\item A gate can only close if there is no ship in between its doors.
	\item A gate can only open if the water level on both sides is equal.
	\item Signal lights can never be off nor indicate hold and pass at the same time.
	\item Signal lights can only indicate pass if the gate is completely opened.
	\item The entering signal can only indicate pass if there is no ship in the lift already.
\end{enumerate}

\subsubsection*{Functionality}
\textit{Basic:}
\begin{enumerate}
	\item After a ship entered the system, this ship should be transported to the other level before any other ship is allowed to enter the system
\end{enumerate}
%\textit{Serving Order:}
%\begin{enumerate}
%	\item If the system is in idle the first ship to arrive at a signal light should get served first
%	\item If the system is not in idle state, a ship is leaving the system and
%	\begin{enumerate}
%		\item there is no other boat waiting, the system should enter idle state
%		\item there is a boat waiting on one side of the lift, it should be transported to the other side
%		\item there are boats waiting on both sides of the lift, then the boat on the current level should get served first
%	\end{enumerate}
%\end{enumerate}
