\section{Translation of the Requirements into Interaction}
\begin{enumerate}
	\item Only one gate can be open at a time	
	\begin{itemize}
		\item An openGate(0) action cannot be followed by an openGate(1) action unless a closeGate(0) action happened in between.
		\item An openGate(1) action cannot be followed by an openGate(0) action unless a closeGate(1) action happened in between.
		
	\end{itemize}
	
	\item Only one valve can be open at a time	
	\begin{itemize}
		\item An openValve(0) action cannot be followed by an openValve(1) action unless a closeValve(0) action happened in between.
		\item An openValve(1) action cannot be followed by an openValve(0) action unless a closeValve(1) action happened in between.
	\end{itemize}
	
	\item A valve and a gate at different levels can never be open at the same time
	\begin{itemize}
		\item An openValve(0) action is not allowed after an openGate(1) action, and visa versa.
		\item An openValve(1) action is not allowed after an openGate(0) action, and visa versa.
	\end{itemize}
	
	\item A gate can only close if there is no ship in between its doors
	\begin{itemize}
		\item A closeGate(gateID) can only be done after gateSensor(gateID, false)
	\end{itemize}
	
	\item A gate can only open if the water level on both sides is equal
	\begin{itemize}
		\item An openGate(1) action can only be done after compareWaterlevel(1.0, true)
		\item An openGate(0) action can only be done after compareWaterlevel(0.0, true)
	\end{itemize}
	
	\item Signal light:
	\begin{enumerate}
		\item The signal can never be off nor indicate hold and pass at the same time
		\begin{itemize}
			\item passSignal(SignalID, true) has to be followed directly by a haltSignal(SignalID, false)
			\item haltSignal(SignalID, true) has to be followed directly by a passSignal(SignalID, false)
			\item passSignal(SignalID, false) can only be issued directly after haltSignal(SignalID, true)
			\item haltSignal(SignalID, false) can only be issued directly after passSignal(SignalID, true)
		\end{itemize}
		\item The signal can only indicate pass if the gate is completely opened
		\begin{itemize}
			\item A passSignal(0.0, true) or passSignal(0.1, true) action can not be done after an openGate(0) action when gateState(0, false)
			\item A passSignal(1.0, true) or passSignal(1.1, true) action can not be done after an openGate(1) action when gateState(1, false)
		\end{itemize}
		\item The entering signal can only indicate pass if there is no ship in the system already
		\begin{itemize}
			\item if shipPresence(0.1, true) or shipPresence(1.1,true) it is not possible to do a passSignal(0.0, true) or passSignal(1.0) action 
		\end{itemize}
	\end{enumerate}
\end{enumerate}

\subsubsection*{Functionality}
\begin{enumerate}
	\item If the system is in idle the first ship to arrive at a signal light should get served first
	\begin{itemize}
		\item if every gateState(gateID, false), compareWaterlevel(0.0, true) and shipPresence(0.0, true), an openGate(0) action will be done, after eventually an openGate(1) action will follow.
		\item if every gateState(gateID, false), compareWaterlevel(0.0, false) and shipPresence(0.0, true), an openValve(0) action will be done, after eventually an openGate(1) action will follow.
		\item if every gateState(gateID, false), compareWaterlevel(1.0, true) and shipPresence(1.0, true), an openGate(1) action will be done after eventually an openGate(0) action will follow.
		\item if every gateState(gateID, false), compareWaterlevel(1.0, false) and shipPresence(1.0, true), an openValve(1) action will be done, after eventually an openGate(0) action will follow.
	\end{itemize}
	\item If the system is not in idle state, a ship is leaving the system and there
	\begin{enumerate}
		\item is no other boat waiting, the system should enter idle state
		\begin{itemize}
			\item if every shipPresence(posID, false) do a haltSignal(signalID, true) for every signalID, a passSignal(signalID, false) for every signalID, followed by a closeGate(0) and closeGate(1) action.
		\end{itemize}
		\item are boats waiting on one side of the lift, the first boat in line gets served
		\begin{itemize}
			\item if only shipPresence(0.0, true), compareWaterlevel(0.0, true), gateState(0, true), a passSignal(0.0) action will be done, after eventually an openGate(1) action will follow.
			\item if only shipPresence(0.0, true), compareWaterlevel(0.0, false), a closeGate(1) action will be done, followed by an openValve(0) action, an openGate(0) action and eventually by an openGate(1) action.
			\item if only shipPresence(1.0, true), compareWaterlevel(1.0, true), gateState(1, true), a passSignal(1.0) action will be done, after eventually an openGate(0) action will follow.
			\item if only shipPresence(1.0, true), compareWaterlevel(1.0, false), a closeGate(0) action will be done, followed by an openValve(1) action, an openGate(1) action and eventually by an openGate(0) action.
		\end{itemize} 
		\item are boats waiting on both sides of the lift, then the first boat on the current level gets served
		\begin{itemize}
			\item if shipPresence(0.0, true), shipPresence(1.0, true), compareWaterlevel0.0, true), an passSignal(0.0,true) action will be done after eventually an openGate(1) action will follow.
			\item if shipPresence(0.0, true), shipPresence(1.0, true), compareWaterlevel1.0, true), an passSignal(1.0,true) action will be done after eventually an openGate(0) action will follow.
		\end{itemize}
	\end{enumerate}
\end{enumerate}

